### 2012-03-18 docs/test_suite/test_suite.tex
update

An automated regression test suite for \maestro\ (or any BoxLib-based
code) written in Python exists in {\tt BoxLib/Tools/C\_util/regtests/}
as {\tt testnew.py}.  The test suite consists of a set of problem
definitions (the \maestro\ problem + their inputs file, etc.).  When
the suite is run the first time, the plotfiles created at the end of
each problem's executation is stored as a benchmark.  After this
initialization, each subsequent run of the test suite compares the
current output of the code, level-by-level and zone-by-zone to the
stored benchmarks (using the {\tt fcompare.f90} routine in {\tt
  AmrPostprocessing/F\_Src/}).  Any differences are flagged as errors.
A web page report is generated by the test suite and provides a
history of the regression testing.  Single-processor and parallel test
problems, compilation tests, self-tests (problems that determine by
themselves whether they were successfully), and testing restarting
from a checkpoint file are supported.

@@

Here {\tt test2} contained inside the {\tt []} is the name of the
problem, as the test suite will refer to it.  {\tt buildDir} is the
path beneath {\tt sourceDir} where the {\tt make} command should be
executed.  The inputs file is given by {\tt inputFile} and the
necessary model file is listed by {\tt aux1File}. (Not all problems
will need this.  Additional auxillary files can be specified via {\tt
  aux2File} and {\tt aux3File}).  Note that {\tt inputFile} and {\tt aux?File} are
specified relative to the {\tt buildDir}. The dimensionality is specified by {\tt dim}.

@@

\begin{figure}[t]
\centering
%\includegraphics[width=5.0in]{CastroVerification/test_suite_day}
\caption{\label{fig:test_suite_date} The test suite output for a
  single day's run.  Each row indicates a separate test, showing
  whether they passed or failed.  Clicking on the test name will give
  more information about that particular test on that day. Note: this
  page is from the {\tt Maestro} code, but a {\tt Castro} test suite
  run will produce similar output.}
\end{figure}

Upon completion of all the runs, a web page for this invocation of the
test suite will be generated (see figure~\ref{fig:test_suite_date}),
as well as pages showing the details for each of the problems run.
Test failures indicate that the current output does not match the stored
benchmarks.

@@

If a bug was introduced into the code recently, then by examing the
test history you can determine the time period in which the bug was
introduced.  The {\tt ChangeLog}s linked to on each test date's webpage
will list all the changes committed to CVS/git up to that point, which is
useful for tracking down the bug.  Once the bug is fixed, rerunning
the suite should generate a `pass'.

>>>>

An automated regression test suite for \maestro\ (or any BoxLib-based
code) written in Python exists in {\tt BoxLib/Tools/C\_util/regtests/}
as {\tt testnew.py}.  The test suite consists of a set of problem
definitions (the \maestro\ problem + their inputs file, etc.).  When
the suite is run the first time, the plotfiles created at the end of
each problem's execution is stored as a benchmark.  After this
initialization, each subsequent run of the test suite compares the
current output of the code, level-by-level and zone-by-zone to the
stored benchmarks (using the {\tt fcompare.f90} routine in {\tt
  AmrPostprocessing/F\_Src/}).  Any differences are flagged as errors.
A web page report is generated by the test suite and provides a
history of the regression testing.  Single-processor and parallel test
problems, compilation tests, self-tests (problems that determine by
themselves whether they were successfully), and testing restarting
from a checkpoint file are supported.

@@

Here {\tt test2} contained inside the {\tt []} is the name of the
problem, as the test suite will refer to it.  {\tt buildDir} is the
path beneath {\tt sourceDir} where the {\tt make} command should be
executed.  The inputs file is given by {\tt inputFile} and the
necessary model file is listed by {\tt aux1File}. (Not all problems
will need this.  Additional auxiliary files can be specified via {\tt
  aux2File} and {\tt aux3File}).  Note that {\tt inputFile} and {\tt aux?File} are
specified relative to the {\tt buildDir}. The dimensionality is specified by {\tt dim}.

@@

Upon completion of all the runs, a web page for this invocation of the
test suite will be generated as well as pages showing the details for
each of the problems run.  Test failures indicate that the current
output does not match the stored benchmarks.

@@

If a bug was introduced into the code recently, then by examining the
test history you can determine the time period in which the bug was
introduced.  The {\tt ChangeLog}s linked to on each test date's webpage
will list all the changes committed to CVS/git up to that point, which is
useful for tracking down the bug.  Once the bug is fixed, rerunning
the suite should generate a `pass'.
